Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-20 manuscript/manuscript.tex
added comment about competing effects figure
tweaks to empirical trees figure

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figures/empirical_trees.pdf}}
\caption{\label{fig:empirical_trees}
\textbf{Effect of site-specific stationary state and $\Gamma\omega$ rate variation on HA branch length estimation.} 
The HA tree is optimized by models from the ExpCM and GY94 families. 
The amino-acid preferences defining the model (ExpCM) or implied by the model (GY94) are shown as logoplots. 
The amino-acid preferences measured by the deep mutational scans defining the ExpCMs were measured in either an H1 background, an H3 background, or were the average measurements from the H1 and H3 scans. 
The circle denotes the H1 clade and the triangle denotes the H3 clade. 
\jdbcomment{You could perhaps do fewer preferences (just a bit fewer), or maybe better break the ExpCM labels onto two lines. Or maybe even better, but model labels above preferences so they can be bigger and maybe in bold, and it will also align the preferences with the y-axis on the plots.}
}
\end{figure}

@@

\skhcomment{I know I was pressing on this a lot, but I think that the three trees in Figure 5 turn out not to be useful as they aren't aligned in a helpful way. So I would suggest instead creating something that is a hybrid between the current Supplementary figure 4A and the Figure 5B. It shows the sequence subsets, and then just shows that the stringency parameter goes down for more diverged alignments. I like the Supplementary figure 4A as it shows the trees most clearly. I like the Figure 5B because it gives the stringency parameters but also shows their actual effects in logos, which is more intuitive than just plotting them on a graph.}

>>>>

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figures/empirical_trees.pdf}}
\caption{\label{fig:empirical_trees}
\textbf{Effect of site-specific stationary state and $\Gamma\omega$ rate variation on HA branch length estimation.} 
The HA tree is optimized by models from the ExpCM and GY94 families. 
The amino-acid preferences defining the model (ExpCM) or implied by the model (GY94) are shown as logoplots. 
The amino-acid preferences measured by the deep mutational scans defining the ExpCMs were measured in either an H1 background, an H3 background, or were the average measurements from the H1 and H3 scans. 
The circle denotes the H1 clade and the triangle denotes the H3 clade. 
}
\end{figure}

@@

\skhcomment{I know I was pressing on this a lot, but I think that the three trees in Figure 5 turn out not to be useful as they aren't aligned in a helpful way. So I would suggest instead creating something that is a hybrid between the current Supplementary figure 4A and the Figure 5B. It shows the sequence subsets, and then just shows that the stringency parameter goes down for more diverged alignments. I like the Supplementary figure 4A as it shows the trees most clearly. I like the Figure 5B because it gives the stringency parameters but also shows their actual effects in logos, which is more intuitive than just plotting them on a graph.}
\skhcomment{Two panels one for H1 and one for H3. Each panel has big tree with the subtrees labeled and the same prefs snippet as fig 4 with the different beta values for each subtree.}
